Modelling BCG vaccination in the UK

### 2019-05-01 index/05-evidence-policy-change.Rmd
added data for sutherland

## Read formated results
## See https://github.com/seabbs/AssessBCGPolicyChange/blob/master/vignettes/paper.Rmd
## for code required to reproduce 
## Chapter is an edited version of the orginal reproducible document.
```

>>>>

## Read formated results
## See https://github.com/seabbs/AssessBCGPolicyChange/blob/master/vignettes/paper.Rmd
## for code required to reproduce 
## Chapter is an edited version of the orginal reproducible document.
##Wordcount:

## Functions for results read in
read_formated <- function(name) {
  path <- file.path("chapters/evidence-policy-change", paste0(name, ".rds"))

  tmp <- readRDS(path)

  return(tmp)
}

load_formated <- function(name) {

  path <- file.path("chapters/evidence-policy-change", paste0(name, ".rda"))

  load(path)
}

## Read in all relevent rda's
rda_list <- c("annual_nots-mw", "annual_nots_tab", "avg-inc", "avg-not",
              "mann-whitney", "max-not",
              "min-not", "model-valid",
              "table-vac-prev")

walk(rda_list, ~ load_formated(.))

```
